Spatial Reasoning and Data Displays

### 2015-03-16 Paper/InfoVis2015/appendix.tex
Appendix fixes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\section{Lineup Performance and Demographic Characteristics}\label{app:categoricalresults}
Table~\ref{tab:ttest-demographics} provides the results of a sequence of linear models fit to the lineup data. Each row in the table represents a single model, with one predictor variable (a factor with two or more levels). Due to sample size considerations, multiple testing corrections were not performed; in addition, the independent variables are correlated: in our sample, males are more likely to have completed Calculus 1, but are also more likely to spend time playing video games. As such, a model including two or more of the significant predictor variables shows all included variables to be nonsignificant. To better understand the effects of these variables, a larger study is necessary. 
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{| Error in eval(expr, envir, enclos): contrasts can be applied only to factors with 2 or more levels}}\end{kframe}% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 16:58:33 2015
\begin{table}[ht]
\centering
\caption{Participant demographics' impact on lineup score. The table below shows each single demographic variable's association with lineup score. STEM major, completion of Calculus I, time spent playing video games, and gender all show some association with score on statistical lineups. \label{tab:ttest-demographics}} 
\begin{tabular}{lrrrr}
  \hline
Variable & DF & Mean.Squared & F.value & p.value \\ 
  \hline
stem & 1 & 401.517 & 14.44 & 0.001 \\ 
  calc\_1 & 1 & 204.569 & 6.15 & 0.018 \\ 
  vidgame\_hrs\_factor & 3 & 108.847 & 3.44 & 0.028 \\ 
  sex & 1 & 140.844 & 4.02 & 0.053 \\ 
  art\_skills & 4 & 75.891 & 2.28 & 0.082 \\ 
  verbal\_skills & 3 & 60.220 & 1.68 & 0.191 \\ 
  math\_science\_research & 1 & 59.670 & 1.60 & 0.214 \\ 
  AutoCAD & 1 & 50.893 & 1.36 & 0.252 \\ 
  age & 1 & 34.434 & 0.91 & 0.348 \\ 
  math\_skills & 3 & 37.039 & 0.98 & 0.416 \\ 
  stats\_class & 1 & 9.062 & 0.23 & 0.631 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 16:58:33 2015
\begin{table}[htb]
\centering
\caption{Importance of principal components in an analysis of four tests of spatial ability: figure classification, paper folding, card rotation, and visual search.\label{tab:PCAvariance4}} 
{\footnotesize
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
Standard deviation & 1.61 & 0.81 & 0.73 & 0.49 \\ 
  Proportion of Variance & 0.64 & 0.16 & 0.13 & 0.06 \\ 
  Cumulative Proportion & 0.64 & 0.81 & 0.94 & 1.00 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 16:58:33 2015
\begin{table}[htb]
\centering
\caption{Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\label{tab:PCArotation4}} 
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
card.rot & 0.55 & -0.19 & -0.38 & 0.72 \\ 
  fig.class & 0.46 & 0.58 & 0.66 & 0.14 \\ 
  folding & 0.52 & 0.33 & -0.53 & -0.59 \\ 
  vis.search & 0.46 & -0.72 & 0.38 & -0.34 \\ 
   \hline
\end{tabular}
\end{table}

@@

{\centering \includegraphics[width=.7\linewidth]{Figure/fig-biplot-pca4-1} 
\includegraphics[width=.7\linewidth]{Figure/fig-biplot-pca4-2}

@@

{\centering \includegraphics[width=.7\linewidth]{Figure/fig-biplots-pca5-1} 
\includegraphics[width=.7\linewidth]{Figure/fig-biplots-pca5-2}

@@

\begin{figure}[ht]
\includegraphics[width=\linewidth]{Figure/fig-lineup-types-scores-1}
\caption{Scatterplots of scaled lineup scores by aptitude test scores. There is some indication that different types of lineup tasks may utilize different visual skills; for instance, QQ-plots with confidence bands may require more skill at mental rotation than QQ-plots without the bands. \label{fig:scatterplottypes}}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{figure}}

@@

\section{Lineup Performance and Demographic Characteristics}\label{app:categoricalresults}
Table~\ref{tab:ttest-demographics} provides the results of a sequence of linear models fit to the lineup data. Each row in the table represents a single model, with one predictor variable (a factor with two or more levels). Due to sample size considerations, multiple testing corrections were not performed; in addition, the independent variables are correlated: in our sample, males are more likely to have completed Calculus 1, but are also more likely to spend time playing video games. As such, a model including two or more of the significant predictor variables shows all included variables to be nonsignificant. To better understand the effects of these variables, a larger study is necessary. 
% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 17:53:53 2015
\begin{table}[ht]
\centering
\caption{Participant demographics' impact on lineup score. The table below shows each single demographic variable's association with lineup score. STEM major, completion of Calculus I, time spent playing video games, and gender all show some association with score on statistical lineups. \label{tab:ttest-demographics}} 
\begin{tabular}{lrrrr}
  \hline
Variable & DF & MeanSq & F & p.val \\ 
  \hline
STEM Major & 1 & 401.517 & 14.44 & 0.001 \\ 
  Calculus 1 & 1 & 204.569 & 6.15 & 0.018 \\ 
  Video Game Hours & 3 & 108.847 & 3.44 & 0.028 \\ 
  Sex & 1 & 140.844 & 4.02 & 0.053 \\ 
  Art Skills & 4 & 75.891 & 2.28 & 0.082 \\ 
  Verbal Skills & 3 & 60.220 & 1.68 & 0.191 \\ 
  STEM Research & 1 & 59.670 & 1.60 & 0.214 \\ 
  AutoCAD & 1 & 50.893 & 1.36 & 0.252 \\ 
  Age & 1 & 34.434 & 0.91 & 0.348 \\ 
  Math Skills & 3 & 37.039 & 0.98 & 0.416 \\ 
  Statistics Class & 1 & 9.062 & 0.23 & 0.631 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 17:53:53 2015
\begin{table}[htb]
\centering
\caption{Importance of principal components in an analysis of four tests of spatial ability: figure classification, paper folding, card rotation, and visual search.\label{tab:PCAvariance4}} 
{\footnotesize
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
Standard deviation & 1.61 & 0.81 & 0.73 & 0.49 \\ 
  Proportion of Variance & 0.64 & 0.16 & 0.13 & 0.06 \\ 
  Cumulative Proportion & 0.64 & 0.81 & 0.94 & 1.00 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

% latex table generated in R 3.1.2 by xtable 1.7-1 package
% Mon Mar 16 17:53:53 2015
\begin{table}[htb]
\centering
\caption{Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\label{tab:PCArotation4}} 
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
card.rot & 0.55 & -0.19 & -0.38 & 0.72 \\ 
  fig.class & 0.46 & 0.58 & 0.66 & 0.14 \\ 
  folding & 0.52 & 0.33 & -0.53 & -0.59 \\ 
  vis.search & 0.46 & -0.72 & 0.38 & -0.34 \\ 
   \hline
\end{tabular}
\end{table}

@@

{\centering \includegraphics[width=.45\linewidth]{Figure/fig-biplot-pca4-1} 
\includegraphics[width=.45\linewidth]{Figure/fig-biplot-pca4-2}

@@

{\centering \includegraphics[width=.45\linewidth]{Figure/fig-biplots-pca5-1} 
\includegraphics[width=.45\linewidth]{Figure/fig-biplots-pca5-2}

@@

\begin{figure*}[ht]\centering
\includegraphics[width=\linewidth]{Figure/fig-lineup-types-scores-1}
\caption{Scatterplots of scaled lineup scores by aptitude test scores. There is some indication that different types of lineup tasks may utilize different visual skills; for instance, QQ-plots with confidence bands may require more skill at mental rotation than QQ-plots without the bands. \label{fig:scatterplottypes}}
\end{figure*}
